---
title: 'Day 2 + Exercise Two '
author: "Dmitrij Petrov"
date: "March 30, 2015"
output:
  html_document:
    fig_caption: yes
    highlight: null
    self_contained: no
    toc: yes
---

#### Load and read excel file.

```{r}

library(xlsx)
library(mi)
library(ggplot2)
datasetM <- read.xlsx("/srv/shiny-server/SemesterProject/Data/DataSet_01.xlsx", sheetIndex = 1, endRow=277)
```

#### Example

Post.ID - ID of a Facebook post

Fanpage Reach -

Earned Reach - The "real" stuff that comes automatically from non-facebook. Cross-sharing. 

Total Reach - Sum of both

X-Match -

Duration - 

Acquaintance - <https://www.academia.edu/2758533/Personal_acquaintance_measure_distinguishing_among_friends_and_good_and_bad_customers>

```{r}
head(datasetM)

summary(datasetM)
```


#### What type of variables we have ? Alles zu diskret

<https://www.wiwiweb.de/statistik/grundbegriff/merkmale/stetige.html>

**Documentation says**:

**fixed** : varaibles that contain only one value

**binary** :  	variables that contain two values

**ordered-categorical** : variables that contain 3 to 5 postive values

**unorderd-categorial** : variables that contain characters or more than 5 postive levels

**positive-continuous** : variables that contain more than 5 postive values, NOT including 0s

**nonnegative** :  	variables that contain more than 5 postive values, including 0s.

**continuous** : 	variables that are not belong to any of the above types

**log-continuous** : 	log-scaled continuous variable

```{r}
# mi.info(datasetM)

cbind(c1 = typecast(datasetM))
```

#### How many cases of each variable do we have ? 

>  0 for female and 1 for male

```{r}
table(datasetM$Gender)

table(datasetM$Duration)

```

#### Likes histogram ?

```{r}
m <- ggplot(datasetM, aes(x=Likes))
m <- m + geom_histogram(binwidth = 0.5)
m <- m + coord_cartesian(xlim = c(0, 40), ylim=c(0,33)) + scale_x_continuous(breaks = seq(0, 40, 1)) 
m <- m + scale_y_continuous(breaks = seq(0, 33, 1))
m <- m + geom_vline(xintercept = mean(datasetM$Likes), size = 2, colour = "red")
m

```

#### Comments histogram ?

```{r}
w <- ggplot(datasetM, aes(x=Comments))
w <- w + geom_histogram(binwidth = 0.5)
w <- w + coord_cartesian(xlim = c(0, 40), ylim=c(0,50)) + scale_x_continuous(breaks = seq(0, 40, 1))
w <- w + scale_y_continuous(breaks = seq(0, 50, 1))
w <- w + geom_vline(xintercept = mean(datasetM$Comments), size = 2, colour = "red")
w
```

#### Relationship between Likes and Comments

Thanks: <http://elkhartgroup.com/tutorials/modelsinr.html>

```{r}
relLC <- lm(Likes ~ Comments, data=datasetM)
relLC

relLC2 <- lm(Comments ~ Total.Reach, data=datasetM)
relLC2


likesComm <- ggplot(datasetM, aes(x=Likes, y=Comments))
likesComm <- likesComm + stat_smooth() + geom_point()
likesComm <- likesComm + geom_abline(intercept = coef(relLC)[1], slope = coef(relLC)[2])
likesComm

# With Gender groupings
likesComm2 <- ggplot(datasetM, aes(x=Likes, y=Comments, color = factor(Gender)))
likesComm2 <- likesComm2 + geom_point() + stat_smooth(method = "lm")
likesComm2

```

Thanks: <http://www.ling.upenn.edu/~joseff/rstudy/summer2010_ggplot2_intro.html>

<http://www.unomaha.edu/mahbubulmajumder/data-science/fall-2014/lectures/05-data-visualization/05-data-visualization.html>

```{r}
likesComm3 <- ggplot(datasetM, aes(x=Likes, y=Comments, color = factor(Gender)))
likesComm3 <- likesComm3 + geom_point() + stat_smooth(method = "lm")
likesComm3 <- likesComm3 + facet_grid(~Duration) # Gender~Duration might be better too
likesComm3
```

#### Relationship between Fan page and Earned Reach


```{r}
# With Gender groupings
fanEarned <- ggplot(datasetM, aes(x=Fanpage.Reach, y=Earned.Reach, color = factor(Gender)))
fanEarned <- fanEarned + geom_point() + stat_smooth(method = "lm")
fanEarned
```


















