---
title: 'Day 1 '
author: "Dmitrij Petrov"
date: "March 30, 2015"
output:
  html_document:
    fig_caption: yes
    self_contained: no
    theme: cerulean
---

### Load and read excel file.

```{r}

library(xlsx)
library(mi)
library(ggplot2)
datasetM <- read.xlsx("/srv/shiny-server/SemesterProject/Data/DataSet_01.xlsx", sheetIndex = 1, endRow=277)
```

### Example

```{r}
head(datasetM)
```

#### What type of variables we have ? Alles zu diskret

<https://www.wiwiweb.de/statistik/grundbegriff/merkmale/stetige.html>

Documentation says 

**fixed** : varaibles that contain only one value

**binary** :  	variables that contain two values

**ordered-categorical** : variables that contain 3 to 5 postive values

**unorderd-categorial** : variables that contain characters or more than 5 postive levels

**positive-continuous** : variables that contain more than 5 postive values, NOT including 0s

**nonnegative** :  	variables that contain more than 5 postive values, including 0s.

**continuous** : 	variables that are not belong to any of the above types

**log-continuous** : 	log-scaled continuous variable

```{r}
# mi.info(datasetM)

cbind(c1 = typecast(datasetM))
```

#### How many cases of each variable do we have ? 

>  0 for female and 1 for male

```{r}
table(datasetM$Gender)

table(datasetM$Duration)

```

#### Likes histogram ?

```{r}
m <- ggplot(datasetM, aes(x=Likes))
m <- m + geom_histogram(binwidth = 0.5)
m <- m + coord_cartesian(xlim = c(0, 40), ylim=c(0,33)) + scale_x_continuous(breaks = seq(0, 40, 1)) 
m <- m + scale_y_continuous(breaks = seq(0, 33, 1))
m

```

#### Comments histogram ?

```{r}
w <- ggplot(datasetM, aes(x=Comments))
w <- w + geom_histogram(binwidth = 0.5)
w <- w + coord_cartesian(xlim = c(0, 40), ylim=c(0,50)) + scale_x_continuous(breaks = seq(0, 40, 1))
w <- w + scale_y_continuous(breaks = seq(0, 50, 1))
w
```

#### Cluster

```{r}

```


